Writing a reproducible paper with RStudio and Quarto

### 2023-04-03 paper.qmd
Update files/links.

---
title: "Writing a reproducible paper with RStudio and Quarto"
author:
  - name: Paul C. Bauer
    orcid: 0000-0002-8382-9724
    email: mail@paulcbauer.de
    affiliations:
      - name: Mannheim Centre for European Social Research
  - name: Camille Landesvatter
    orcid: 0000-0003-0156-5364
    email: camille.landesvatter@uni-mannheim.de
    affiliations:
      - name: Mannheim Centre for European Social Research
format:
  html: default
  pdf:
    number-sections: true
    colorlinks: true
    keeptex: true
    include-in-header: 
      text: |
        \usepackage{booktabs}
        \usepackage{siunitx}
        \newcolumntype{d}{S[
            input-open-uncertainty=,
            input-close-uncertainty=,
            parse-numbers = false,
            table-align-text-pre=false,
            table-align-text-post=false
         ]}
date: 'last-modified'
date-format: '[This version:] MMMM D, YYYY [<br>(First version: February  16, 2023)]'
abstract: 'This paper provides a template to write a reproducible scientific paper with RStudio and Quarto. It falls into a series of other templates, namely using RMarkdown [@Bauer2018-dl] (see [here](https://osf.io/k8jhx/)) and Pagedown [@Bauer2021-dl] (see [here](https://osf.io/q395s)). Below we outline some of the "tricks"/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document. The underlying files which produce this document can be [downloaded here](https://drive.google.com/drive/folders/1jDPpXdX6dusXpKkXEhDGujWDGf52TaxD?usp=sharing). We are convinced that in the future there will be many improvements and developments with regards to RStudio and Quarto. We intend to update this file when we discover more convenient code. You can follow any updates on the [github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_with_quarto/).'
bibliography: references.bib
csl: american-sociological-association.csl
tbl-cap-location: top
number-sections: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
editor:
  mode: source
---

@@

-   ...download the 3 input files we created --- `paper.qmd`, `references.bib` and `data.csv` --- from [this folder](https://drive.google.com/drive/u/0/folders/1eT_9WaineZRB-nw-cQhNOy16sWhd_t2s). Ignore the other files.
-   ...finally store all files from above together in one folder (and use this folder as your working directory later on).

@@

-   `paper.qmd` (the underlying R Markdown file).
-   `references.bib` (the bibliography).
    -   We use paperpile to manage references and export the `.bib` file into the folder that contains the `.qmd` file.
-   `data.csv` (some raw data).

[Download these files](https://drive.google.com/drive/u/0/folders/1eT_9WaineZRB-nw-cQhNOy16sWhd_t2s) and save them into a folder. Close R/Rstudio and directly open `paper.qmd` with RStudio. Doing so assures that the working directory is set to the folder that contains `paper.qmd` and the other files.[^1]

@@

Below we import an exemplary dataset (you can find `data.csv` in the [folder](https://drive.google.com/drive/u/0/folders/1eT_9WaineZRB-nw-cQhNOy16sWhd_t2s) with the other files).

>>>>

---
title: "Writing a reproducible paper with RStudio and Quarto"
author:
  - name: Paul C. Bauer
    orcid: 0000-0002-8382-9724
    email: mail@paulcbauer.de
    affiliations:
      - name: Mannheim Centre for European Social Research
  - name: Camille Landesvatter
    orcid: 0000-0003-0156-5364
    email: camille.landesvatter@uni-mannheim.de
    affiliations:
      - name: Mannheim Centre for European Social Research
format:
  html: default
  pdf:
    number-sections: true
    colorlinks: true
    keeptex: true
    include-in-header: 
      text: |
        \usepackage{booktabs}
        \usepackage{siunitx}
        \newcolumntype{d}{S[
            input-open-uncertainty=,
            input-close-uncertainty=,
            parse-numbers = false,
            table-align-text-pre=false,
            table-align-text-post=false
         ]}
date: 'last-modified'
date-format: '[This version:] MMMM D, YYYY [<br>(First version: February  16, 2023)]'
abstract: 'This paper provides a template to write a reproducible scientific paper with RStudio and Quarto. It falls into a series of other templates, namely using RMarkdown [@Bauer2018-dl] (see [here](https://osf.io/k8jhx/)) and Pagedown [@Bauer2021-dl] (see [here](https://osf.io/q395s)). Below we outline some of the "tricks"/code (e.g., referencing tables, sections etc.) we had to figure out to produce this document. The underlying files which produce this document can be [downloaded here](https://github.com/paulcbauer/Writing_a_reproducable_paper_with_quarto/) (click on Code -> Download ZIP). We are convinced that in the future there will be many improvements and developments with regards to RStudio and Quarto. We intend to update this file when we discover more convenient code. You can follow any updates on the [github repository](https://github.com/paulcbauer/Writing_a_reproducable_paper_with_quarto/).'
bibliography: references.bib
csl: american-sociological-association.csl
tbl-cap-location: top
number-sections: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
editor:
  mode: source
---

@@

- ...download the 4 input files we created (see below) from [github](https://github.com/paulcbauer/Writing_a_reproducable_paper_with_quarto/) (click on Code -> Download ZIP). Ignore/delete the other files.

		- `paper.qmd`
		- `references.bib`
		- `american-sociological-association.csl`
		- `data.csv`

- ...finally store all files from above together in one folder (and use this folder as your working directory later on).

@@

-   `paper.qmd` (the underlying R Markdown file).
-   `references.bib` (the bibliography).
    -   We use paperpile to manage references and export the `.bib` file into the folder that contains the `.qmd` file.
- `american-sociological-association.csl` (the bibliography style)
-   `data.csv` (some raw data).

[Download these files from github]((https://github.com/paulcbauer/Writing_a_reproducable_paper_with_quarto/) (click on Code -> Download ZIP) and save them into a folder. Close R/Rstudio and directly open `paper.qmd` with RStudio. Doing so assures that the working directory is set to the folder that contains `paper.qmd` and the other files.[^1]

@@

Below we import an exemplary dataset (you can find `data.csv` in the [github repository]((https://github.com/paulcbauer/Writing_a_reproducable_paper_with_quarto/) with the other files).
